\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-03-16 k-planar.tex
Added anote
Suggestion

@@

>>>>

\note{PM}{I have significantly simplified this section, which should make the referees happy. I will read it very carefully again tomorrow}

@@

\note{PM}{Consider a change of notation:   Replace $F$ with $C$.  (I was using $F$ before to be consistent with the previous section, but that notation is gone now.)}
